Draft Research pt1

### 2019-03-05 draftResearch_pt1.Rmd
Working on compiling up eligible positions into a comma separated string or vector

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
source("R/yahoo_api.R")
library(tidyverse)
library(rlist)
```

# Position Eligibility

```{r}
get_json("users;use_login=1/games;game_keys=mlb/players") -> players

players %>%
  content() -> players_content

players_content$fantasy_content$users$`0`$user[[2]]$games$`0`$game[[2]]$players[c(1:25)] -> players_list

players_list %>% rlist::list.stack()

players %>% list.load()

@@

# Projection Data

Info for getting depth chart projections:
[Batters](https://www.fangraphs.com/projections.aspx?pos=all&stats=bat&type=fangraphsdc&team=0&lg=all&players=0)

[Pitchers](https://www.fangraphs.com/projections.aspx?pos=all&stats=pit&type=fangraphsdc&team=0&lg=all&players=0)

Download to CSV via:
`javascript:__doPostBack('ProjectionBoard1$cmdCSV','')`

Downloading manually for now...

```{r}
pitchers <- read_csv("data/depthChartProjections_pitchers_20190220.csv")

batters <- read_csv("data/depthChartProjections_batters_20190220.csv")

pitchers
batters
```

>>>>

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
source("R/yahoo_api.R")
library(tidyverse)
```

# Position Eligibility
```{r}
(get_players(50) -> tst_results)

tst_results %>%
  select(starts_with("eligible_positions")) %>%
  transpose() %>%
  lapply(as.character) %>%
  lapply(function(x) x[!is.na(x)]) -> pos_complete

# add list rows representing new column as new column on prior df?
tst_results %>%
  add_column(pos_complete) %>%
  select(1, pos_complete)

@@
